Global patterns of forest autotrophic carbon fluxes

### 2020-08-07 manuscript/manuscript draft.Rmd
issue #118

We first examined the relationship between latitude and C fluxes (*Q1*; Table 1). 
We tested models with latitude as a first-order linear, second-order polynomial, and logarithmic term. 
For brevity, we henceforth refer to first-order linear models as "linear" and second-order polynomial models as "polynomial".
We selected as the best model that with the highest $\Delta$ AIC relative to a null model with no fixed term, with the qualification that a polynomial model was considered an improvement over a linear model only if it reduced the AIC value by 2.0 or more.

@@

All major carbon fluxes decreased with latitude (Fig. 2; Table S2). Latitude was a strong predictor for many of the carbon fluxes, particularly the larger fluxes (Table S2). Specifically, latitude explained 64% of variation in GPP (n = 243, p<0.0001), 50% in NPP (n = 161, p<0.0001) and 44% in ANPP (n = 278, p<0.0001). The C fluxes that were most poorly predicted by latitude were $BNPP_{fine.root}$ ($R^2$=0.17) and $ANPP_{stem}$ ($R^2$=0.18). The relationship with latitude was best fit by the first-order linear model, with the exception of NPP and $R_{root}$, for which a logarithmic model was a slightly -- but not significantly -- better fit.

@@

All fluxes increased with $MAT$ (all p<0.05; Figs. 3-4, S4-S5, Table S2). 
For eight of the nine fluxes, this relationship was linear.
For only one variable, $BNPP$, did a lognormal fit provide an improvement over a first-order linear relationship, though this was not significant ($\Delta$AIC <2).
As with latitude, $MAT$ tended to explain more variation in the larger fluxes ($GPP$, $NPP$, $ANPP$, $R_{auto}$) and $ANPP_{foliage}$ (all $R^2$> 0.4) than in subsidiary and belowground fluxes ($ANPP_{stem}$, $R_{root}$, $BNPP_{fine.root}$; all $R^2$< 0.25).

>>>>

We first examined the relationship between latitude and C fluxes (*Q1*; Table 1). 
We tested models with latitude as a first-order linear, second-order polynomial, and logarithmic term. 
For brevity, we henceforth refer to first-order linear models as "linear" and second-order polynomial models as "polynomial".
We selected as the best model that with the highest $\Delta$ AIC relative to a null model with no fixed term, with the qualification that a polynomial model was considered an improvement over a linear model only if it reduced the AIC value by 2.0 or more.
In addition, pairwise comparisons of $R^2$ values were carried out for a selection of pairs of C fluxes to test for differences among variables in the proportion of variation explained by latitude and climate. Models were run on data from sets of sites that were common to each pair, in order to account for variation in the number of data points included.

@@

All major carbon fluxes decreased with latitude (Fig. 2; Table S2). Latitude was a strong predictor for many of the carbon fluxes, particularly the larger fluxes (Table S2, S6). Specifically, latitude explained 64% of variation in GPP (n = 243, p<0.0001), 50% in NPP (n = 161, p<0.0001) and 44% in ANPP (n = 278, p<0.0001). The C fluxes that were most poorly predicted by latitude were $BNPP_{fine.root}$ ($R^2$=0.17) and $ANPP_{stem}$ ($R^2$=0.18). The relationship with latitude was best fit by the first-order linear model, with the exception of NPP and $R_{root}$, for which a logarithmic model was a slightly -- but not significantly -- better fit.

@@

All fluxes increased with $MAT$ (all p<0.05; Figs. 3-4, S4-S5, Table S2). 
For eight of the nine fluxes, this relationship was linear.
For only one variable, $BNPP$, did a lognormal fit provide an improvement over a first-order linear relationship, though this was not significant ($\Delta$AIC <2).
As with latitude, $MAT$ tended to explain more variation in the larger fluxes ($GPP$, $NPP$, $ANPP$, $R_{auto}$) and $ANPP_{foliage}$ (all $R^2$> 0.4) than in subsidiary and belowground fluxes ($ANPP_{stem}$, $R_{root}$, $BNPP_{fine.root}$; all $R^2$< 0.25; Table S6).
